\section{Hypotheses}

\begin{frame}{Hypotheses (1)}
    \begin{itemize}
        \setlength\itemsep{1.5em}

        \item What is the relation between the amount of requests that RoboPizza receives and the waiting time for customers?
            \begin{itemize}
                \item $H_1$: The waiting time increases with the amount of requests.
                \item $H_0$: The waiting time does \textbf{not} increase with the amount of requests.
            \end{itemize}

        \item Are robots on the road more when there are more requests in the system?
            \begin{itemize}
                \item $H_1$: Robots are on the road more when there are more requests in the system.
                \item $H_0$: Robots are \textbf{not} on the road more when there are more requests in the system.
            \end{itemize}
    \end{itemize}
\end{frame}

\begin{frame}{Hypotheses (2)}
    \begin{itemize}
        \setlength\itemsep{1.5em}

        \item Does increasing the amount of robots decrease the customer waiting time when there are many requests?
            \begin{itemize}
                \item $H_1$: Increasing the amount of robots decreases the customer waiting time when there are many requests.
                \item $H_0$: Increasing the amount of robots does \textbf{not} decrease the customer waiting time when there are many requests.
            \end{itemize}

        \item How does the amount of robots impact the workload (occupancy rate) of the charging station?
            \begin{itemize}
                \item $H_1$: A larger amount of robots increases the workload of the charging station.
                \item $H_0$: A larger amount of robots does \textbf{not} increase the workload of the charging station.
            \end{itemize}
    \end{itemize}
\end{frame}

\begin{frame}{Hypotheses (3)}
    \begin{itemize}
        \setlength\itemsep{1.5em}

        \item What is the relation between the amount of charging robots and the amount of clients we have to decline?
            \begin{itemize}
                \item $H_1$: The amount of charging robots has no influence on the amount of clients that have to be declined.
                \item $H_0$: The amount of charging robots \textbf{influences} on the amount of clients that have to be declined.
            \end{itemize}

            \item How do waiting times change as the amount of road works change (dynamism)?
                \begin{itemize}
                    \item $H_1$: Waiting times increase as the amount of road works increase.
                    \item $H_0$: Waiting times do \textbf{not} increase as the amount of road works increase.
                \end{itemize}
    \end{itemize}
\end{frame}

\begin{frame}{Hypotheses (4)}
    \begin{itemize}
        \setlength\itemsep{1.5em}

        \item How do waiting times change as the amount of pickup locations change (dynamism)?
            \begin{itemize}
                \item $H_1$: Waiting times decrease as the amount of pickup locations increase.
                \item $H_0$: Waiting times do \textbf{not} decrease as the amount of pickup locations increase.
            \end{itemize}
    \end{itemize}
\end{frame}
