\section{Research questions and hypotheses}

\begin{frame}[allowframebreaks]{Research questions and hypotheses}
    \begin{itemize}
        \item What is the relation between the amount of requests that RoboPizza receives and the waiting time for customers?
        \begin{itemize}
                \item $H_1$: The waiting time increases with the amount of requests.
                \item $H_0$: The waiting time does \textbf{not} increase with the amount of requests.
        \end{itemize}

        \item Are robots on the road more often when there are more requests in the system?
        \begin{itemize}
                \item $H_1$: Robots are on the road more often when there are more requests in the system.
                \item $H_0$: Robots are \textbf{not} on the road more when there are more requests in the system.
        \end{itemize}

        \item Does increasing the amount of robots decrease the customer waiting time when there are many requests?
        \begin{itemize}
                \item $H_1$: Increasing the amount of robots decreases the customer waiting time when there are many requests.
                \item $H_0$: Increasing the amount of robots does \textbf{not} decrease the customer waiting time when there are many requests.
        \end{itemize}

        \item How does the amount of robots impact the average workload (occupancy rate) of the charging station?
        \begin{itemize}
                \item $H_1$: A larger amount of robots increases the average workload of the charging station.
                \item $H_0$: A larger amount of robots does \textbf{not} increase the average workload of the charging station.
        \end{itemize}

        \item How do waiting times change as the amount of road works changes (dynamism)?
        \begin{itemize}
            \item $H_1$: Waiting times increase as the amount of road works increase.
            \item $H_0$: Waiting times do \textbf{not} increase as the amount of road works increase.
        \end{itemize}

    \item How do waiting times change as the amount of pickup locations changes (dynamism)?
    \end{itemize}
\end{frame}
